%-------------------------
% https://www.overleaf.com/latex/templates/rezume/kfrvqywfkwjs
% Rezume, a latex resume template for developers
% Author : Nanu Panchamurthy
% Based off of: https://github.com/sb2nov/resume
% License : MIT

% Hope this resume template helps you land an awesome job. If you found this helpful, please consider starring the github repo here, .
%-------------------------



%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{verbatim} % reimplements the "verbatim" and "verbatim*" environments

\usepackage{titlesec} % provides an interface to sectioning commands i.e. custom elements

\usepackage{color} % provides both foreground and background color management

\usepackage{enumitem} % provides control over enumerate, itemize and description

\usepackage{fancyhdr} % provides extensive facilities for constructing headers, footers and also controlling their use

\usepackage{tabularx} % defines an environment tabularx, extension of "tabular" with an extra designator x, paragraph like column whose width automatically expands to fill the width of the environment

\usepackage{latexsym} % provides mathematical symbols

\usepackage{marvosym} % provides martin vogel's symbol font which contains various symbols

\usepackage[empty]{fullpage} % sets margins to one inch and removes headers, footers etc..

\usepackage[hidelinks]{hyperref} % removes color and shadow of hyperlinks

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks

\usepackage[english]{babel} % provides culturally determined typographical rules for wide range of languages
%-----------------------------------------

\input glyphtounicode % converts glyph names to unicode
\pdfgentounicode=1 % ensures pdfs generated are ats readable

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro} % uses the font source sans pro
\urlstyle{same} % changes url font from default urlfont to font being used by the document
%-----------------------------------------


%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % set page style to one configured by fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % sets thickness of linerule under header to zero
\renewcommand{\footrulewidth}{0in} % sets thickness of linerule over footer to zero

\setlength{\tabcolsep}{0in} % sets thickness of column separator in tables to zero

% origin of the document is one inch from the top and from and the left
% oddsidemargin and evensidemargin both refer to the left margin
% right margin is indirectly set using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % sets width of text area in the page to one inch
\addtolength{\textheight}{1.0in} % sets height of text area in the page to one inch

\raggedbottom{} % makes all pages the height of current page, no extra vertical space added
\raggedright{} % makes all pages the width of current page, no extra horizontal space added
%------------------------------------------


%--------SECTIONING COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command is the sectioning command to be redefined
% shape is the style of the font; scshape stands for small caps style
% format is the format to be applied to whole title- label and text; absent here
% label defines the label
% sep is the horizontal separation between label and title body
% before-code is the code to be executed before
% after-code is the code to be executed after

\titleformat{\section}
{\scshape\large}{}
{0em}{\color{blue}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------


%--------REDEFINITIONS----------------
% redefines the style of the bullet point
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% redefines the underline depth to 2pt
\renewcommand{\ULdepth}{2pt}
%-------------------------------------


%--------CUSTOM COMMANDS--------------
%\vspace{} defines a vertical space of given size, modifying this in custom commands can help stretch or shrink resume to remove or add content

% resumeItem renders a bullet point
\newcommand{\resumeItem}[1]{
	\item\small{#1}
}

% commands to start and end itemization of resumeItem, rightmargin set to 0.11in to avoid the overflow of resumetItem beyond whatever resumeItemHeading is being used
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
	\newcommand{\resumeItemListEnd}{\end{itemize}}

% resumeSectionType renders a bolded type to be used under a section, used as skill type here, middle element is used to keep ":"s in the same vertical line
\newcommand{\resumeSectionType}[3]{
	\item\begin{tabular*}{0.96\textwidth}[t]{
			p{0.15\linewidth}p{0.02\linewidth}p{0.81\linewidth}
		}
		\textbf{#1} & #2 & #3
	\end{tabular*}\vspace{-2pt}
}

% resumeTrioHeading renders three elements in three columns with second element being italicized and first element bolded, can be used for projects with three elements
\newcommand{\resumeTrioHeading}[3]{
	\item\small{
		\begin{tabular*}{0.96\textwidth}[t]{
				l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r
			}
			\textbf{#1} & \textit{#2} & #3
		\end{tabular*}
	}
}

% resumeQuadHeading renders four elements in a two columns with the second row being italicized and first element of first row bolded, can be used for experience and projects with four elements
\newcommand{\resumeQuadHeading}[4]{
	\item
	\begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}
}

% resumeQuadHeadingChild renders the second row of resumeQuadHeading, can be used for experience if different roles in the same company need to added
\newcommand{\resumeQuadHeadingChild}[2]{
	\item
	\begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{\small#1} & {\small#2} \\
	\end{tabular*}
}

% commands to start and end itemization of resumeQuadHeading, lefmargin for left indent of 0.15in for resumeItems
\newcommand{\resumeHeadingListStart}{
	\begin{itemize}[leftmargin=0.15in, label={}]
	}
	\newcommand{\resumeHeadingListEnd}{\end{itemize}}
%-------------------------------------------


%__________________RESUME____________________
% You can rearrange sections in any order you may prefer
\begin{document}
	
	%-----------CONTACT DETAILS------------------
	% Make sure all the details are correct, you can add more links in the first row of second column if needed
	
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Huge Daniel Precioso, PhD \vspace{2pt}} & % row = 1, col = 1
		Location: Madrid, Spain \\ % row = 1, col = 2
		\href{https://danielprecioso.com}{\uline{danielprecioso.com}} $|$ % row = 2, col = 1
		\href{https://www.linkedin.com/in/daniel-precioso-garcelan}{\uline{LinkedIn}} $|$ % row = 2, col = 1
		\href{https://github.com/daniprec}{\uline{GitHub}} % row = 2, col = 1
		$|$ \href{https://www.researchgate.net/profile/Daniel-Precioso-Garcelan}{\uline{ResearchGate}} % row = 2, col = 1
		& % row = 2, col = 1
		Email: \href{mailto:daniel.precioso@ie.edu}{\uline{daniel.precioso@ie.edu}} \\ % row = 2, col = 2
		& % row = 3, col = 1
		ORCID: \href{https://orcid.org/0000-0003-3836-1429}{\uline{0000-0003-3836-1429}} \\ % row = 3, col = 2
	\end{tabular*}
	%--------------------------------------------
	
	
	%-----------SUMMARY--------------------------
	% Keep this short, simple and straigth to point
	
	\section{Data Scientist}
	% \small{
	 I have \textbf{more than 6 years of experience} in \textbf{knowledge transfer} between academia and industry. My diverse skill set includes problem-solving, automation, and simplifying complex ideas, using my expertise in \textbf{Data Science (DS)} and \textbf{Machine Learning (ML)}. This unique combination of skills has enabled me to address challenges across various sectors such as healthcare, energy, aerospace, and logistics.
	 
	 My goal is to not only solve industry challenges but also advance technology by publishing academic research. I enjoy sharing ideas at conferences and exhibitions and teaching new generations of scientists and professionals. I am passionate about collaboration, mentoring teammates, and transforming scientific ideas into industrial projects.
		% }
	%--------------------------------------------
	
	
	%--------------SKILLS------------------------
	% Add or remove resumeSectionTypes according to your needs
	
	\section{Technical Skills}
	\resumeHeadingListStart{}
	\resumeSectionType{Languages}{:}{Python, Matlab, R}
	\resumeSectionType{Libraries}{:}{NumPy, Pandas, scikit-learn, TensorFlow, JAX, Streamlit}
	\resumeSectionType{Dev Tools}{:}{Visual Studio Code, Git, Github}
	\resumeSectionType{Academic Tools}{:}{Latex, Overleaf, Blackboard, Wordpress}
	\resumeHeadingListEnd{}
	%--------------------------------------------
	
	
	%-----------EXPERIENCE-----------------------
	% Distill all your talking points to small bullet points which follow the pattern "challenge-action-result" for maximum efficiency. Try to quantify (use numbers) your points whenver possible, highlist words of importance
	
	\section{Experience}
	\resumeHeadingListStart{}
	
	\resumeQuadHeading{Postdoctoral Researcher \& Adjunct Professor}{Sep 2023 -- Present}
	{IE University}{Madrid, Spain}
	\resumeItemListStart{}
	\resumeItem{Contributed to three research projects delivering measurable impact:
		\begin{itemize}
			\item Built climate impact models simulating insurance risk under SSP scenarios that VIG used for portfolio strategy.
			\item Implemented Kolmogorov-Arnold Networks (KANs) for weather forecasting, improving prediction accuracy.
			\item Designed optimization algorithms that reduce ship GHG emissions through real-time weather-based routing.
		\end{itemize}}
	\resumeItem{Built and maintained IE Research Datalab's website, increasing research visibility and collaboration opportunities.}
	\resumeItem{Delivered technical courses to 100+ students with consistently high satisfaction ratings.}
	\resumeItemListEnd{}
	
	\resumeQuadHeading{COO}{Apr 2023 -- Present}
	{Canonical Green}{Madrid, Spain}
	\resumeItemListStart{}
	\resumeItem{Built and deployed DS solutions that enable maritime clients to optimize routes, reducing carbon emissions by 10\%.}
	\resumeItem{Delivered technical presentations to investors and stakeholders, translating complex algorithms into business value.}
	\resumeItemListEnd{}
	
	\resumeQuadHeading{Data Scientist}{Sep 2022 -- Apr 2023}
	{Komorebi AI}{Madrid, Spain}
	\resumeItemListStart{}
	\resumeItem{Cleaned and processed 500K+ data points from raw sensor data, enabling accurate fish population monitoring.}
	\resumeItem{Designed and deployed gradient-boosted and CNN models that achieved 90\%+ accuracy in real-time tuna detection.}
	\resumeItem{Built an interactive dashboard that leadership used daily for operational decisions, reducing analysis time by 80\%.}
	\resumeItemListEnd{}
	
	\resumeQuadHeading{Predoctoral Research Staff}{Sep 2019 -- Aug 2022}
	{University of C\'adiz}{C\'adiz, Spain}
	\resumeItemListStart{}
	\resumeItem{Built ML models for Industry 4.0 applications in energy monitoring and non-destructive testing, reducing operational costs for industrial partners.}
	\resumeItem{Partnered with Spain's Health Alerts Centre to create COVID-19 ICU forecasting models that informed national policy decisions during the pandemic.}
	\resumeItem{Delivered presentations at international conferences, translating complex research into actionable insights for diverse audiences.}
	\resumeItem{Published 5 peer-reviewed papers in Q1/Q2 journals, advancing the field of applied ML and DS.}
	\resumeItemListEnd{}
	
	\resumeQuadHeading{Junior Data Scientist}{Jan 2019 -- Jun 2019}{Foqum}{Madrid, Spain}
	
	\resumeHeadingListEnd{}
	%---------------------------------------------
	
	
	%-----------EDUCATION-------------------------
	% Mention your CGPA, if its good, in the first row of second column
	
	\section{Education}
	\resumeHeadingListStart{}
	
	\resumeQuadHeading{Phd in Computer Engineering}{Sep 2019 -- Jul 2023}
	{University of C\'adiz}{C\'adiz, Spain}
	
	\resumeQuadHeading{MSc in Statistical and Computational Information Processing}{Sep 2018 -- Jul 2019}
	{Universidad Polit\'ecnica de Madrid}{Madrid, Spain}
	
	\resumeQuadHeading{Degree in Physics}{Sep 2014 -- Jul 2018}
	{Complutense University of Madrid}{Madrid, Spain}
	
	\resumeHeadingListEnd{}
	%---------------------------------------------
	
	
	%-----------PROJECTS--------------------------
	% Use resumeQuadHeading if four elements are feasible (ex: demo video link), else use resumeTrioHeading. Keep the bullet points simple and concise and try to cover wide variety of skills you have used to build these projects
	
	\section{Projects}
	\resumeHeadingListStart{}
	
	\resumeTrioHeading{KAN4Met}{Machine Learning, Meteorology}{IE University}
	\resumeItemListStart{}
	\resumeItem{Implemented Kolmogorov-Arnold Networks for weather forecasting, advancing ML-based prediction accuracy.}
	\resumeItem{Contributed to research team that secured funding from Spanish Ministerio de Ciencia, Educación y Universidades.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{Insurance and Tech}{Data Science, Actuarial Science}{IE University}
	\resumeItemListStart{}
	\resumeItem{Built predictive models analyzing climate impact on insurance risk that VIG used for data-driven portfolio strategies.}
	\resumeItem{Contributed to industry-academic partnership with Vienna Insurance Group (VIG), translating complex climate models into actionable business insights.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{Weather Navigation}{Mathematical Optimization, Maritime Transport}{IE University}
	\resumeItemListStart{}
	\resumeItem{Designed optimization algorithms that reduced maritime fuel consumption by 10\% while improving route safety and cutting carbon emissions.}
	\resumeItem{Contributed to research team that secured substantial funding from BBVA Foundation and Spanish Agencia Estatal (grant TED2021-129455B-I00).}
	\resumeItem{Built and maintained the official project website \href{https://weathernavigation.com/}{\uline{https://weathernavigation.com/}}.}
	\resumeItem{Presented technology to \href{https://www.youtube.com/watch?v=T2VRDSczxVM&t}{\uline{the European Parliament}}, positioning the innovation for EU-wide adoption.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{Tun-AI}{Deep Learning, Fishing Industry}{Komorebi AI}
	\resumeItemListStart{}
	\resumeItem{Partnered with Satlink to build AI-powered tuna monitoring systems that automated detection with 90\%+ accuracy.}
	\resumeItem{Transformed 500K+ raw echosounder readings into clean, structured datasets that powered ML models.}
	\resumeItem{Deployed gradient-boosted trees and CNNs optimized for real-time fish detection on cloud, enabling instant monitoring decisions.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{NeoCam}{Computer Vision, Healthcare}{Univesidad de C\'adiz}
	\resumeItemListStart{}
	\resumeItem{Built a contactless monitoring system using Luxonis OAK-D cameras that enabled health experts to track newborn vitals in NICUs.}
	\resumeItem{Won 2nd place globally at \href{https://opencv.org/opencv-ai-competition-2021/\#regional-winners}{\uline{OpenCV AI Competition 2021}} among 1,400+ teams.}
	\resumeItem{Co-inventor on \href{https://drive.google.com/file/d/1AN-C6Wb77trgd3riLIXcsKpQlfIfOlGk/view?usp=sharing}{\uline{official patent registration}} in 2023, protecting intellectual property for future commercialization.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{COVID-19}{Time Series Forecasting, Healthcare}{Univesidad de C\'adiz}
	\resumeItemListStart{}
	\resumeItem{Partnered with Spain's Coordination Centre for Health Alerts to build ICU occupancy forecasting models that informed resource allocation during peak pandemic periods.}
	\resumeItem{Analyzed non-pharmaceutical interventions (NPIs) impact on COVID-19 spread, providing evidence-based recommendations that shaped public health policy.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{UCAnFly}{Computer Modeling, Astrophysics}{Univesidad de C\'adiz}
	\resumeItemListStart{}
	\resumeItem{Built MATLAB simulations modeling Earth's electromagnetic field effects on gravitational test mass for space-based detectors like \href{https://www.elisascience.org/}{\uline{LISA}}.}
	\resumeItem{Contributed electromagnetic modeling expertise to multidisciplinary team selected by ESA's \href{https://www.esa.int/Education/CubeSats_-_Fly_Your_Satellite}{\uline{Fly Your Satellite!}} programme.}
	\resumeItemListEnd{}
	
	\resumeTrioHeading{ATENEA}{Computer Vision, Industrial Automation}{Univesidad de C\'adiz}
	\resumeItemListStart{}
	\resumeItem{Built ML and NLP solutions for Airbus D\&S that automated production processes, reducing manual inspection time.}
	\resumeItem{Contributed to industry partnership funded by CDTI Interconnecta program.}
	\resumeItemListEnd{}
	
	\resumeHeadingListEnd{}
	%--------------------------------------------
	
	
	%----------------OTHERS----------------------
	% You can add your acheivements, accolades, certifications etc. here.
	
	\section{Courses and Certifications}
	\resumeItemListStart{}
	
	\resumeItem{\href{https://www.coursera.org/learn/wharton-ai-in-education-leveraging-chatgpt-for-teaching}{\uline{AI in Education: Leveraging ChatGPT for Teaching}} (Coursera)}
	
	\resumeItem{\href{https://openbadgefactory.com/v1/assertion/4d76a8035a509add2f9b01f1c19cdb9a0eef56ca.html}{\uline{Machine learning in Python with scikit-learn}} (France Universit\'e Num\'erique)}
	
	\resumeItem{\href{https://drive.google.com/file/d/1hNx8BzQxnWpydmgg9RoCtc44FBE6HSEG/view?usp=sharing}{\uline{XV Modeling Week at UCM (Coordinator)}} (UCM)}
	
	\resumeItem{\href{https://drive.google.com/file/d/1GrqmPLSJoitdC7otmq_SRfqXVbEOuW_F/view?usp=sharing}{\uline{Fly your Satellite - 3 CDR Virtual Workshop}} (ESA)}
	
	\resumeItem{\href{https://www.coursera.org/account/accomplishments/specialization/WXQQSYVFLA78}{\uline{TensorFlow in Practice Specialization}} (Coursera)}
	%\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/FE4HNB2LFVRU}{\uline{Convolutional Neural Networks in TensorFlow}} (Coursera)}
	%\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/XG8F2HMXUH4V}{\uline{Introduction to TensorFlow for Artificial Intelligence, Machine Learning, and Deep Learning}} (Coursera)}
	%\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/FPHZBNAU29ZK}{\uline{Natural Language Processing in TensorFlow}} (Coursera)}
	%\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/DKX6PA6UFBQC}{\uline{Sequences, Time Series and Prediction}} (Coursera)}
	
	\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/JEZRF6VKSWUE}{\uline{Applied Social Network Analysis in Python}} (Coursera)}
	\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/HKSAYBJFPQGU}{\uline{Applied Machine Learning in Python}} (Coursera)}
	\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/PMFZNFG755X3}{\uline{Applied Text Mining in Python}} (Coursera)}
	\resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/2SDFQS2HSAE3}{\uline{Introduction to Data Science in Python}} (Coursera)}
	
	\resumeItemListEnd{}
	
	\section{Publications}
	\resumeItemListStart{}
	\resumeItem{\href{https://doi.org/10.1016/j.marstruc.2025.103863}{\uline{New analysis in the preliminary design for LNG and LPG ships}}. Marine Structures, Elsevier, 2025 (Q1).}
	\resumeItem{\href{https://benchmark.weathernavigation.com/static/pdfs/benchmarks-1.pdf}{\uline{HADAD: Hexagonal A-Star with Differential Algorithm Designed for weather routing}}. Ocean Engineering, 2024 (Q1)}
	\resumeItem{\href{https://doi.org/10.1007/s40314-024-02756-w}{\uline{Hybrid Search method for Zermelo's navigation problem}}. Computational and Applied Mathematics, 2024 (Q2)}
	\resumeItem{\href{https://doi.org/10.3354/meps14338}{\uline{Aggregation dynamics of tropical tunas around drifting floating objects based on large-scale echo-sounder data}}. Marine Ecology Progress Series, 2023 (Q1)}
	\resumeItem{\href{https://doi.org/10.21203/rs.3.rs-1732801/v1}{\uline{Effectiveness of non-pharmaceutical interventions in nine fields of activity to decrease SARS-CoV-2 transmission (Spain, September 2020-May 2021)}}. Frontiers in Public Health, 2023 (Q1)}
	\resumeItem{\href{https://doi.org/10.21203/rs.3.rs-1923023/v1}{\uline{Thresholding Methods in Non-Intrusive Load Monitoring}}. The Journal of Supercomputing, 2023 (Q2)}
	\resumeItem{\href{https://doi.org/10.1109/JBHI.2023.3240245}{\uline{NeoCam: An edge-cloud platform for non-invasive real-time monitoring in neonatal intensive care units}}. IEEE Journal of Biomedical and Health Informatics, 2023 (Q1)}
	\resumeItem{\href{https://doi.org/10.1016/j.fishres.2022.106263}{\uline{TUN-AI: Tuna biomass estimation with Machine Learning models trained on oceanography and echosounder FAD data}}. Fisheries Research, 2022 (Q2)}
	%\resumeItem{\href{}{\uline{}}}
	\resumeItemListEnd{}
	%--------------------------------------------
	
\end{document}
\begin{document}

\maketitle

\section{Introduction}

\end{document}
